NGO analysis

### 2022-07-26 Dashboard/report.Rmd
OrOr in CEO plot.

# Printing the plot if the data are available
if (sum(!is.na(htmldata$lederlonn)) != 0 |
  sum(!is.na(htmldata$leder_annen_godtgjorelse)) != 0) {
  CEO_plot
}
```

>>>>

# Printing the plot if the data are available
if (sum(!is.na(htmldata$lederlonn)) != 0 ||
  sum(!is.na(htmldata$leder_annen_godtgjorelse)) != 0) {
  CEO_plot
}
```
